Irt plot extra

### 2022-02-10 manuscript.Rmd
rafael's tibble is now banched.

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Our sample size exceeds these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:

```{r fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
```

- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`

For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

>>>>

Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics. Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses. (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items. For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result. Our sample size exceeds these requirements.
We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
Participants reported a diverse range of geographic location
Participants indicated filling out the online survey from a diverse range of geographic locations. Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).

```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
```

```{r rafael2, eval=FALSE, include=FALSE}
# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
```
